---
title: "isomiR annotation"
author: "Lorena Pantano"
date: "`r date()`"
output:
    md_document:
        variant: gfm
        toc: false
---


```{r setup-iso, echo=FALSE}
library(knitr)
library(rmarkdown)
opts_chunk$set(tidy=TRUE, highlight=T, figalign="center",
 fig.height=5, fig.width=9, message=F, error=F, warning=F)
```


```{r load-iso}
library(tidyverse)

parsing = .%>% 
    separate(name, c("fasta", "mature", "position", "trimming", "mut", "ext", "counts"), sep ="_") %>% 
    separate(trimming, c("iso5p", "iso3p"), sep = ":") %>% 
    mutate(correct_mir = mir == mature,
           correct_add = (ext != "add:null" & add != "0") | (ext == "add:null" & add == "0"),
           correct_change = (mut != "mut:null" & mism != "0") | (mut == "mut:null" & mism == "0"),
           correct_5p = (iso5p != "0" & t5 != "0") | (iso5p == "0" & t5 == "0"),
           correct_3p = (iso3p != "0" & t3 != "0") | (iso3p == "0" & t3 == "0"),
           correct_iso = correct_add & correct_change & correct_5p & correct_3p,
           num_5p = ifelse(grepl("[ATGC]", t5), -1 * nchar(t5), 0),
           num_5p = ifelse(grepl("[atcg]", t5), nchar(t5), num_5p),
           num_3p = ifelse(grepl("[ATGC]", t3), nchar(t3), 0),
           num_3p = ifelse(grepl("[atcg]", t3), -1 * nchar(t3), num_3p))
    

data31 <- read.table("sim.21.hsa.3.1.mirna", header=T, stringsAsFactors = F)  %>% 
    parsing()


data3 <- read.table("sim.21.hsa.3.0.mirna", header=T, stringsAsFactors = F)  %>% 
    parsing()

data <- bind_rows(data3 %>% mutate(version = "3.0"),
                  data31 %>% mutate(version = "3.1"))

```

# Overview

I simulated a bunch of isomirs that can have the following variation:

* starts at different position than the reference miRNA: t5
* ends at different position than the reference miRNA: t3
* have a mutation: muts
* have nt addition at the end: add


# Detection

Correct isomir annotation for miraligner.

```{r iso}
library(ggplot2)
ggplot(data, aes(correct_mir, fill = version)) +
    geom_bar(position = "dodge") +
    scale_fill_brewer(palette = "Set1") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


#Accuracy

* `correct_iso` is True when the isomiRs is annotated to the correct miRNA


```{r acc-iso}
ggplot(data, aes(correct_iso, fill = version)) +
    geom_bar(position = "dodge") +
    scale_fill_brewer(palette = "Set1") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))

mutate(data, exact_5p = num_5p == iso5p) %>%
ggplot(aes(exact_5p, fill = version)) +
    geom_bar(position = "dodge") +
    scale_fill_brewer(palette = "Set1") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))

mutate(data,exact_3p = num_3p == iso3p) %>%
#    filter(ext == "add:null") %>% 
ggplot(aes(exact_3p, fill = version)) +
    geom_bar(position = "dodge") +
    scale_fill_brewer(palette = "Set1") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
